### 2018-09-04 pilot_manuscript.Rmd
working on paper

##write it back out
write.csv(newdata, "overalldata.csv", row.names = F)

@@

##separate them into h low, h high until you have ten categories 
#harm/care
original_mfd$h2hi[35:112] = NA 
original_mfd$h2hi[1:34] = c("benefit", "care", "defend", "guard", "preserve",
                      "protect", "safe", "shelter", "sympathetic",
                      "sympathies", "benefits", "benefitted",
                      "benefitting", "cares", "cared", "caring","defends", 
                      "defending","defended", "guards", "guarded",
                      "guarding","preserves",
                      "preserved", "preserving", "protects", "protected",
                      "protecting", "protection",  
                      "safely", "safer", "shelters", 
                      "sheltered", "sheltering")
original_mfd$h2lo[61:112] = NA
original_mfd$h2lo[1:60] = c("abuse", "attack", "cruel", "crush",
                      "damage", "danger", "destroy", "fight", "harm",
                      "hurt", "kill", "ruin", "spurn", "stomp", "suffer",
                      "violent", "war","abusive",
                      "abuser","abused","abusing","damaged",
                      "damaging","attacked","attacking","attacker",
                      "attacks","attackers","crushes",
                      "crushing", "crushed", "dangerous","detroys", 
                      "destroyed", "destroying",
                      "fights", "fought", "fighting","harms", 
                      "harmed", "harming", "hurts",
                      "hurting", "kills", "killed", "killing",
                      "ruins", "ruined", "ruining", "spurns", 
                      "spurned", "spurning", "stomps", "stomped",
                      "stomping", "suffers", "suffered", "suffering",
                      "violence", "warring")

#fairness/reciprocity
original_mfd$f2hi[41:112] = NA
original_mfd$f2hi[1:40] = c("balance", "constant", "equal", "equate", "even",
                      "fair", "honest", "just", "justify", "reason",
                      "right", "tolerate", "impartial", "balances", 
                      "balanced", "balancing",
                      "equals", "equaled", "equaling", "equates", "equated",
                      "equating", "evens", "evened", "evening","fairness",
                      "honesty", "impartiality", "justice", "justifies", 
                      "justified", "justifying", "reasons",
                      "reasoned", "reasoning", "rights", "tolerates",
                      "tolerated", "tolerating", "toleration")
original_mfd$f2lo[25:112] = NA
original_mfd$f2lo[1:24] = c("bias", "discriminate", "exclude", "favor",
                      "prefer", "prejudice", "biased", "biases", "discriminates", 
                      "discriminated", "discriminating", "discrimination",
                      "excludes", "excluded", "excluding", 
                      "favors", "favored", "favoring", "prefers", "preferred", "preferring",
                      "prejudices", "prejudiced", "prejudicing")

#ingroup/loyalty
original_mfd$i2hi[30:112] = NA
original_mfd$i2hi[1:29] = c("collect", "community", "family", "fellow",
                      "group", "member", "nation", "side", "together",
                      "trait", "unite", "collects", 
                      "collected", "collecting", "collective",
                      "communities", "families", "fellows",
                      "groups", "grouped", "grouping",
                      "members", "nations", "sides",
                      "togetherness", "traits", "unites", 
                      "united", "uniting")
original_mfd$i2lo[19:112] = NA 
original_mfd$i2lo[1:18] = c("deceive", "desert", "foreign", "individual",
                      "deceives", "deceived", "deceiving",
                      "deception", "deceptions", "deserts", "deserted",
                      "deserting", "desertion", "foreigners",
                      "indviduals", "indvidualize", "individualized",
                      "individualizing")

#authority/respect
original_mfd$a2hi[86:112] = NA
original_mfd$a2hi[1:85] = c("abide", "authority", "class", "command",
                      "control", "defer", "duty", "faith", "father", "honor",
                      "law", "lead", "legal", "mother", "obey", 
                      "order", "permit", "position", "preserve",
                      "respect", "revere", "serve", "tradtition", "trait",
                      "abides", "abided", "abiding", "authorities",
                      "classes", "classed", "classing", "command",
                      "commanded", "commanding", "controls", "controlled",
                      "controlling","defers", "deferred", "deferring", "deference",
                      "duties","faiths", "fathers", "fathered", "fathering",
                      "honors", "honored", "honoring", "laws", "leads",
                      "leading", "mothers", "mothered", "mothering",
                      "obeys", "obeyed", "obeying", "orders", 
                      "ordered", "ordering", "permits",
                      "permitted", "permitting", "positions", "positioned",
                      "positioning", "preserves", "preserved", "preserving",
                      "preservation", "respects",
                      "respected", "respecting", "respectful", "reveres",
                      "revered", "revering", "reverence", "serves", "served",
                      "serving", "traditions", "traditional", "traits")
original_mfd$a2lo[28:112] = NA
original_mfd$a2lo[1:27] = c("defect", "defy", "desert","oppose", 
                      "protest", "refuse", "defects", "defected", 
                      "defecting","defies", "defied", "defying", "defiance", "deserts",
                      "deserted", "deserting", "desertion", "opposes", "opposed",
                      "opposing", "protests", "protested", "protesting",
                      "refuses", "refused", "refusing", "refusal")

#purity/sanctity
original_mfd$p2hi[32:112] = NA
original_mfd$p2hi[1:31] = c("abstain", "church", "clean", "innocent", "modest",
                      "preserve", "pure", "right", "sacred", "whole",
                      "abstains", "abstained", "abstaining", "abstinence",
                      "churches", "cleans", "cleaned", "cleaning", "cleanse",
                      "cleanliness", "innocence", "modesty", "preserves", "preserved",
                      "preserving", "preservation", "purity", "rights", 
                      "sacredness", "wholeness", "wholesome")
original_mfd$p2lo[30:112] = NA
original_mfd$p2lo[1:29] = c("adultery", "dirt", "disease", "disgust", "gross",
                      "promiscuous", "ruin", "sick", "sin", "trash",
                      "adulteries", "adulterous", "adulterer", "adulterers",
                      "dirty", "diseases", "diseased", "disgusts", 
                      "disgusted", "disgusting", "grossness", "promiscuity",
                      "promiscuities", "ruins", "ruined","ruining", 
                      "sickness", "sicknesses", "sins")
```

@@

```{r new_data, include = FALSE}
#take final$stemmed column loop over this
#Harm
harm_final_data = data.frame("URL" = NA, "Source" = NA, "word" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA"])]

>>>>

##write it back out
#write.csv(newdata, "overalldata.csv", row.names = F)

@@

# ##separate them into h low, h high until you have ten categories 
# #harm/care
# original_mfd$h2hi[35:112] = NA 
# original_mfd$h2hi[1:34] = c("benefit", "care", "defend", "guard", "preserve",
#                       "protect", "safe", "shelter", "sympathetic",
#                       "sympathies", "benefits", "benefitted",
#                       "benefitting", "cares", "cared", "caring","defends", 
#                       "defending","defended", "guards", "guarded",
#                       "guarding","preserves",
#                       "preserved", "preserving", "protects", "protected",
#                       "protecting", "protection",  
#                       "safely", "safer", "shelters", 
#                       "sheltered", "sheltering")
# original_mfd$h2lo[61:112] = NA
# original_mfd$h2lo[1:60] = c("abuse", "attack", "cruel", "crush",
#                       "damage", "danger", "destroy", "fight", "harm",
#                       "hurt", "kill", "ruin", "spurn", "stomp", "suffer",
#                       "violent", "war","abusive",
#                       "abuser","abused","abusing","damaged",
#                       "damaging","attacked","attacking","attacker",
#                       "attacks","attackers","crushes",
#                       "crushing", "crushed", "dangerous","detroys", 
#                       "destroyed", "destroying",
#                       "fights", "fought", "fighting","harms", 
#                       "harmed", "harming", "hurts",
#                       "hurting", "kills", "killed", "killing",
#                       "ruins", "ruined", "ruining", "spurns", 
#                       "spurned", "spurning", "stomps", "stomped",
#                       "stomping", "suffers", "suffered", "suffering",
#                       "violence", "warring")
# 
# #fairness/reciprocity
# original_mfd$f2hi[41:112] = NA
# original_mfd$f2hi[1:40] = c("balance", "constant", "equal", "equate", "even",
#                       "fair", "honest", "just", "justify", "reason",
#                       "right", "tolerate", "impartial", "balances", 
#                       "balanced", "balancing",
#                       "equals", "equaled", "equaling", "equates", "equated",
#                       "equating", "evens", "evened", "evening","fairness",
#                       "honesty", "impartiality", "justice", "justifies", 
#                       "justified", "justifying", "reasons",
#                       "reasoned", "reasoning", "rights", "tolerates",
#                       "tolerated", "tolerating", "toleration")
# original_mfd$f2lo[25:112] = NA
# original_mfd$f2lo[1:24] = c("bias", "discriminate", "exclude", "favor",
#                       "prefer", "prejudice", "biased", "biases", "discriminates", 
#                       "discriminated", "discriminating", "discrimination",
#                       "excludes", "excluded", "excluding", 
#                       "favors", "favored", "favoring", "prefers", "preferred", "preferring",
#                       "prejudices", "prejudiced", "prejudicing")
# 
# #ingroup/loyalty
# original_mfd$i2hi[30:112] = NA
# original_mfd$i2hi[1:29] = c("collect", "community", "family", "fellow",
#                       "group", "member", "nation", "side", "together",
#                       "trait", "unite", "collects", 
#                       "collected", "collecting", "collective",
#                       "communities", "families", "fellows",
#                       "groups", "grouped", "grouping",
#                       "members", "nations", "sides",
#                       "togetherness", "traits", "unites", 
#                       "united", "uniting")
# original_mfd$i2lo[19:112] = NA 
# original_mfd$i2lo[1:18] = c("deceive", "desert", "foreign", "individual",
#                       "deceives", "deceived", "deceiving",
#                       "deception", "deceptions", "deserts", "deserted",
#                       "deserting", "desertion", "foreigners",
#                       "indviduals", "indvidualize", "individualized",
#                       "individualizing")
# 
# #authority/respect
# original_mfd$a2hi[86:112] = NA
# original_mfd$a2hi[1:85] = c("abide", "authority", "class", "command",
#                       "control", "defer", "duty", "faith", "father", "honor",
#                       "law", "lead", "legal", "mother", "obey", 
#                       "order", "permit", "position", "preserve",
#                       "respect", "revere", "serve", "tradtition", "trait",
#                       "abides", "abided", "abiding", "authorities",
#                       "classes", "classed", "classing", "command",
#                       "commanded", "commanding", "controls", "controlled",
#                       "controlling","defers", "deferred", "deferring", "deference",
#                       "duties","faiths", "fathers", "fathered", "fathering",
#                       "honors", "honored", "honoring", "laws", "leads",
#                       "leading", "mothers", "mothered", "mothering",
#                       "obeys", "obeyed", "obeying", "orders", 
#                       "ordered", "ordering", "permits",
#                       "permitted", "permitting", "positions", "positioned",
#                       "positioning", "preserves", "preserved", "preserving",
#                       "preservation", "respects",
#                       "respected", "respecting", "respectful", "reveres",
#                       "revered", "revering", "reverence", "serves", "served",
#                       "serving", "traditions", "traditional", "traits")
# original_mfd$a2lo[28:112] = NA
# original_mfd$a2lo[1:27] = c("defect", "defy", "desert","oppose", 
#                       "protest", "refuse", "defects", "defected", 
#                       "defecting","defies", "defied", "defying", "defiance", "deserts",
#                       "deserted", "deserting", "desertion", "opposes", "opposed",
#                       "opposing", "protests", "protested", "protesting",
#                       "refuses", "refused", "refusing", "refusal")
# 
# #purity/sanctity
# original_mfd$p2hi[32:112] = NA
# original_mfd$p2hi[1:31] = c("abstain", "church", "clean", "innocent", "modest",
#                       "preserve", "pure", "right", "sacred", "whole",
#                       "abstains", "abstained", "abstaining", "abstinence",
#                       "churches", "cleans", "cleaned", "cleaning", "cleanse",
#                       "cleanliness", "innocence", "modesty", "preserves", "preserved",
#                       "preserving", "preservation", "purity", "rights", 
#                       "sacredness", "wholeness", "wholesome")
# original_mfd$p2lo[30:112] = NA
# original_mfd$p2lo[1:29] = c("adultery", "dirt", "disease", "disgust", "gross",
#                       "promiscuous", "ruin", "sick", "sin", "trash",
#                       "adulteries", "adulterous", "adulterer", "adulterers",
#                       "dirty", "diseases", "diseased", "disgusts", 
#                       "disgusted", "disgusting", "grossness", "promiscuity",
#                       "promiscuities", "ruins", "ruined","ruining", 
#                       "sickness", "sicknesses", "sins")

@@

```{r new_data, include = FALSE}

###harm
#read in the harm total words from the mtmm project
harm_all = read.csv("harm_words_total.csv", stringsAsFactors = F)

harm_final_data = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA)

@@

#only pull the words in the dataset for each foundation
temp2 = temp[temp$Var1 %in% unique(harm_all$words[harm_all$words != "" & harm_all$words != "NA" & !is.na(harm_all$words)]), ]
